Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-23 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
updated robot related work

Typical approaches to spatial representation for mobile robots tend to focus on localization, and thus mostly represent the world uniformly without subdivision into meaningful (semantic) units \cite{Thrun02a}. When a more structured representation is required (e.g., for behavior planning or human-robot interaction), topological maps (i.e., graphs of connected regions) are usually built on top of these metric representations using various landmark-detection techniques to segment regions, e.g. door detection \cite{Hawes/etal:2009b} or clustering of perceptual features \cite{Peltason/etal:2009a}. While capable of recognizing regions, these approaches do not consider the semantic information necessary for identifying context-dependent spatial regions. While steps have been taken toward incorporating this knowledge  (i.e. the types of objects present and their arrangement) into spatial representations, current approaches fall short of representing the types of regions discussed in this work. For example, a number of systems attempt to recognize the category of a room by the objects present within it \cite{Hawes/etal:2010b} (largely ignore location), and others are able to mediate their behavior when certain functional contexts are detected (e.g. the areas near doors \cite{Zender2008a}).

>>>>

% robots and space

Typical approaches to spatial representation for mobile robots tend to focus on localization, and thus mostly represent the world uniformly without subdivision into meaningful (semantic) units \cite{Thrun02a}. When a more structured representation is required, many turn to Kuipers' Spatial Semantic Hierarchy~\cite{Kuipers:2000}. This paper follows in this tradition, adding CDSRs to his qualitative topological representations. Whilst mobile robots exist which can determine the type of a room from the objects in it ~\cite{Hanheide/etal:2010a,Galindo/etal:2005a}, they only concern themselves with types of whole rooms, and cannot represent regions within rooms. This is also true for those systems which use some elements of QSR~\cite{aydemir2011icra}. The need for an autonomous system to ground references to human-generated descriptions of space has been recognised in domains where a robot must be instructed to perform a particular task, however existing systems are restricted to purely geometrically-defined regions~\cite{Tellex:2011,Dzifcak/etal:2009,brenneretal07ijcai}.
